---
title: "MT5000 Final Assignment"
author: "Cian Cahalane"
date: 29/04/23
format: html
editor: visual
echo: false
warning: false
message: false
---

```{r}
library(tidyverse)


unicef_metadata <- read.csv("unicef_metadata.csv")
countries <- c("China", "India", "Russia", "Brazil")
unicef_GDP_2016 <- unicef_metadata %>%
  filter(year == 2016, country %in% countries) %>% select(country, gdp = "GDP.per.capita..constant.2015.US..")

ggplot(data = unicef_GDP_2016) +
  aes(x = country, y = gdp) +
  geom_bar(stat = "identity", fill = "lightgreen") +
  labs(title = "comparative GDP", x = "Country", y = "GDP") +
  theme_classic()
```

#  This bar chart compares the GDP between Brazil, China, India and Russia, it is apparent from the chart that India has only acquired a fraction of the GDP in comparison to the other countries.

```{r}
library(tidyverse)
library(maps)

unicef_indicator_1 <- read.csv("unicef_indicator_1.csv")
world_map <- map_data("world")

unicef_2016 <- unicef_indicator_1 %>%
  filter(time_period == 2016, obs_value > 0) %>% 
  select(country, obs_value)

map_obs_2016 <- full_join(fortify(world_map), unicef_2016, by = c("region" = "country"))

ggplot(data = map_obs_2016) +
  aes(x = long, y = lat, group = group, fill = obs_value, color = obs_value) +
  geom_polygon() +
  scale_fill_gradient(low = "lightblue", high = "blue") +
  labs(title = "Worldwide OBS Value", x = "", y = "") +
  theme_classic()
```

# Please refer to the top observation measure only.

This world map chart displays the percentage of population using unsanitary water. The top obs_value indicator displays countries who have a higher percentage is dark blue while countries light blue have a lower percentage.
